On the application of microwave acoustic resonant viral inactivation \thanks{I would be delighted to include any criticisms or comments anyone may have; preferably leave them on the GitHub issues page, or email therobotist@gmail.com, @0xDBFB7 on Twitter, or irc.0xDBFB7.com:6667 \#covid.}

### 2020-08-22 documents/paper.tex
Integrated amp progress

Protein net charges extracted from protein sequences compiled by the proteome-pI database \cite{ProteomepI2017} and UniProt using localCIDER \cite{CIDER2017} \ghfile{biology/data/net_charge.py}.

>>>>

Protein net charges extracted from primary protein sequences compiled by the proteome-pI database \cite{ProteomepI2017} and UniProt using localCIDER \cite{CIDER2017} \ghfile{biology/data/net_charge.py}.
